Safe Transferable Regions

### 2016-07-04 paper/type-inference.tex
theorem for type inference?
constraint generation

\paragraph{Constraint Generation.}
The constraint generation algorithm is a direct adaption of the type checker:
each type checking rule is modified to produce a set of constraints that must hold
for the type checker to succeed.
%
Fig.~\ref{fig:constraint-gen} illustrates this for the object allocator \C{new} construct.
%
The appendix presents a more detailed algorithm that performs the elaboration and
constraint generation in a single integrated pass.

>>>>

\paragraph{Constraint Generation.}
The constraint generation algorithm is a direct adaption of the type checker:
each type checking rule is modified to produce a set of constraints that must hold
for the type checker to succeed.
%
Fig.~\ref{fig:constraint-gen} illustrates this for a couple of rules.
The algorithm proceeds top-down, analyzes an expression $e$ in a context
$\exptycx{\ralloc}{\env}$, and returns a type $\tau$ and a set of constraints $C$
(expressed in the rules as $\exprok {\exptycx{\ralloc}{\env}} {e} {\tau} {C}$ ),
indicating that the expression will have a type $\tau$ provided the constraints $C$ hold.
%
The appendix presents a more detailed algorithm that performs the elaboration and
constraint generation in a single integrated pass.
